---
title: "HW4"
output: html_notebook
---

### 1. 

```{r}
# load the data
pulse = read.csv("../data/Pulse.csv")
```

T-test for the slope:

$H_0 \; : \; \beta_1 = 0$

$H_1 \; : \; \beta_1 \ne 0$

```{r}
# t-test
fit_lm = lm("Rest ~ Hgt", data=pulse)
summary(fit1)
```

p-value is low, therefore reject $H_0$ in favor of $H_1$.

<br>

ANOVA test for significance:

$H_0 \; : \; \beta_1 = 0$

$H_1 \; : \; \beta_1 \ne 0$

```{r}
anova(fit_lm)
```

p-value is low, therefore reject $H_0$ in favor of $H_1$.

<br>

T-test for Correlation:
$H_0 \; : \; \rho = 0$

$H_1 \; : \; \rho \ne 0$

```{r}
cor.test(pulse$Rest, pulse$Hgt, method="pearson")
```

p-value is low, therefore reject $H_0$ in favor of $H_1$.

<br>

### 2. Population model

$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + \epsilon \,, \: \: \epsilon \sim \mathcal{N}(0, \sigma^2)$

### 3. Fit regression model for $X_1$, $X_2$, and $X_3$

```{r}
fit_muli = lm("Rest ~ Hgt + Wgt + Smoke", data=pulse)
summary(fit_muli)
```

#### 3-(a). $\hat{Rest} = 111.022 - 0.606(Hgt) - 0.013(Wgt) + 5.803(Smoke)$

<br>

#### 3-(b). There is a positive linear trend with coefficient 5.803 if the data case belongs to the smokers group, else 0.

<br>

#### 3-(c).
```{r}
rest_hat = 111.022 - 0.606*65 - 0.013*150 + 5.803*1
rest_hat
```

<br>

3-(d).

$H_0 \; : \; \beta_1 = \beta_2 = \beta_3 = 0$

$H_1 \; : \; At \: least \: one \: \beta_i \ne 0 \: (for \: i=1, 2, 3)$