---
output: pdf_document
---

## B27 \
Hector G. Flores Rodriguez

### Stats 110 - HW 4 \
October 26, 2017

<br>

### 1. 

```{r}
# load the data
pulse = read.csv("../data/Pulse.csv")
```

T-test for the slope:

$H_0 \; : \; \beta_1 = 0$

$H_1 \; : \; \beta_1 \ne 0$

```{r}
# t-test
fit_lm = lm("Rest ~ Hgt", data=pulse)
summary(fit_lm)
```

p-value is low, therefore reject $H_0$ in favor of $H_1$.

<br>

ANOVA test for significance:

$H_0 \; : \; \beta_1 = 0$

$H_1 \; : \; \beta_1 \ne 0$

```{r}
anova(fit_lm)
```

p-value is low, therefore reject $H_0$ in favor of $H_1$.

<br>

T-test for Correlation:
$H_0 \; : \; \rho = 0$

$H_1 \; : \; \rho \ne 0$

```{r}
cor.test(pulse$Rest, pulse$Hgt, method="pearson")
```

p-value is low, therefore reject $H_0$ in favor of $H_1$.

<br>

### 2. Population model

$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + \epsilon \,, \: \: \epsilon \sim \mathcal{N}(0, \sigma^2)$

<br>

### 3. Fit regression model for $X_1$, $X_2$, and $X_3$

```{r}
fit_multi = lm("Rest ~ Hgt + Wgt + Smoke", data=pulse)
summary(fit_multi)
```

#### 3-(a). $\hat{Rest} = 111.022 - 0.606(Hgt) - 0.013(Wgt) + 5.803(Smoke)$

<br>

#### 3-(b). There is a positive linear trend with coefficient 5.803 if the data case belongs to the smokers group, else 0.

<br>

#### 3-(c).
```{r}
rest_hat = 111.022 - 0.606*65 - 0.013*150 + 5.803*1
rest_hat
```

<br>

#### 3-(d).

$H_0 \; : \; \beta_1 = \beta_2 = \beta_3 = 0$

$H_1 \; : \; At \: least \: one \: \beta_i \ne 0 \: (for \: i=1, 2, 3)$

<br>

### 4.

```{r}
anova(fit_multi)
```

#### 4-(a).

$SSTotal = 1346.2 + 0.0 + 756.0 + 20764.5 = 22866.7$

$SSE = 20764.5$

$SSModel = 2102.2$

<br>

#### 4-(b). 

$SSTotal = 22866.7$

$SSModel = 1346.2$

$SSE = 22866.7 - 1346.2 = 21520.5$


### 5.

$H_0 \; : \; \beta_1 = 0$

$H_1 \; : \; \beta_1 \ne 0$

```{r}
summary(fit_multi)
```

#### 5-(a). 
p-value is low, therefore reject $H_0$ in favor of $H_1$. Hence, there is sufficient evidence to suggest that height is a significant predictor of resting pulse rate.

<br>

#### 5-(b).
The significance of height decreased after adding Wgt and Smoke. Hence adding more terms may be overfitting the model.

<br>

### 6.
$\beta_0 =$ intercept of Rest

$\beta_1 =$ slope of Rest against Wgt

$\beta_2 =$ slope of Rest against Smoke

$Rest = \beta_0 + \beta_1 Wgt + \beta_2 Smoke + \epsilon \,, \: \: \epsilon \sim \mathcal{N}(0, \sigma^2)$

<br>

### 7.
```{r}
fit_wgt_smoke = lm("Rest ~ Wgt + Smoke", data=pulse)
summary(fit_wgt_smoke)
```

$H_0 \; : \; \beta_2 = 0$

$H_1 \; : \; \beta_2 \ne 0$

Low p-value for Smoke, hence there is significant evidence that the intercepts are different.

### 8.
$\beta_0 =$ intercept of Rest

$\beta_1 =$ slope of Rest against Wgt

$\beta_2 =$ slope of Rest against Smoke

$\beta_3 =$ slope of Rest against the interaction of Wgt and Smoke


$Rest = \beta_0 + \beta_1 Wgt + \beta_2 Smoke +  \beta_3 Wgt*Smoke + \epsilon \,, \: \: \epsilon \sim \mathcal{N}(0, \sigma^2)$

### 9.

$H_0 \; : \; \beta_3 = 0$

$H_1 \; : \; \beta_3 \ne 0$