---
output:
  pdf_document: default
  html_document: default
---


## B27 \
Hector G. Flores Rodriguez

### Stats 110 - HW 3 \
October 24, 2017

<br>

### 1. Create new data set called *NewPrices* by removing the row with the outlier

```{r}
textprices = read.csv("../data/TextPrices.csv")
NewPrices = textprices[-4,]
```

<br>

#### 1-(a). Use summary command in R to provide summaries of the two variables \
for the original data set and the new data set.

```{r}
# With outlier
summary(textprices)
```
```{r}
# Without outlier
summary(NewPrices)
```

<br>

#### 1-(b). 
The mean number of pages for the data without outlier is: **466.8**

The predicted price for the mean number of pages would be: **$62.83** 

<br>

### 2. Find the $R^2$ using the TextPrices data and again using the NewPrices data.

```{r}
# R-squared value for textprices
tp_fit = lm("Price ~ Pages", data=textprices)
summary(tp_fit)
```

```{r}
# R-squared value for NewPrices
np_fit = lm("Price ~ Pages", data=NewPrices)
summary(np_fit)
```

<br>

#### 2-(a).
$R_{TextPrices}^{2} = 0.6766$

$R_{NewPrices}^{2} = 0.7341$

$73\%$ of the variation in book prices (in NewPrice data set) is explained by the number of pages.

<br>

#### 2-(b).
The NewPrice data set does a better job in prediction since it captures more of the variance than the original data set.

<br>


### 3. Exercise 2.15 with NewPrices data

#### 3-(a).

```{r}
mu_price = data.frame(Pages=450)
predict(np_fit, mu_price, interval="confidence")
```

**A 95% C.I. is [50.126, 70.523]**

<br>

#### 3-(b).
```{r}
predict(np_fit, mu_price, interval="predict")
```

**A 95% P.I. is [4.558, 116.091]**

<br>

#### 3-(c).
```{r}
mean(c(4.558, 116.091))
mean(c(50.126, 70.523))
```

**The midpoint of the two intervals are the same since they both should be the
value of $\hat{y}$ given by OLS.**

<br>

#### 3-(d).
**The P.I. width is much larger than the C.I. This makes sense since the prediction interval takes into account uncertainty for individual observations rather than the mean value**

<br>

#### 3-(e).
**The mean number of pages: 466.8**

<br>

#### 3-(f).
```{r}
pages1500 = data.frame(Pages=1500)
predict(np_fit, pages1500, interval="predict")
```

**A 95% P.I. for a 1500-page textbook is [150.420, 283.907]. We don't have a 95% C.I since we are predicting outside the range of the data we have available.**

<br>

### 4. Exercise 2.10 pg 82

#### 4-(a). Decrease the width of the prediction interval

#### 4-(b). Increase the width of the P.I.

#### 4-(c). Increase the width of the P.I.

#### 4-(d). Increase the width of the P.I.

<br>

### 5. Exercise 2.17, (b) and (c)

#### 5-(b).
```{r}
sparrows = read.csv("../data/Sparrows.csv")
sparrow_fit = lm("Weight ~ WingLength", data=sparrows)
summary(sparrow_fit)
```

**61.39% of the variation in weight is explained by WingLength**

#### 5-(c).
Provide the ANOVA table that partitions the total variablility in weight and interpret the F-test.
```{r}
anova(sparrow_fit)
```

**The F statistic is the same as the $t^2$ for $\beta_{1}=0$ vs $\beta_{1} \neq 0$. Hence, there is significant evidence that there is a linear trend**

<br>

### 6. Exercise 2.44

#### 6-(a).
$\hat{\beta_{1}} = r \frac{s_x}{s_y} = (0.701)(\frac{104807}{657}) = 111.826$

$\hat{\beta_{0}} = \bar{y} - \hat{\beta_{1}} \bar{x} = 247235 - (111.826)(2009) = 22576.57$

$\therefore \: \hat{y} = 22576.57 + 111.826x$

<br>

#### 6-(b).
$r^2 = 0.491401$

**49.1% of the variation in gate counts is explained by enrollements.**

<br>

#### 6-(c).
$\hat{y} = 22576.57 + 111.826(1445) = 184165.1$

<br>

#### 6-(d).

$e = 130000 - (22576.57 + 111.826(2200)) = -138593.8$

<br>

### 7. Skin Cancer example shown in class on Oc 16

#### 7-(a).

$\hat{\beta_1} = -5.9776$

$SE\{\hat{\beta_1}\} = 0.5984$

$MSE = RSE^2 = 365.5744$

$SSX = \frac{MSE}{SE\{\hat{\beta_1}\}^2} = 610.9198$

$\hat{y} = 389.894 - (5.9776)(33.7) = 188.44888$

<br>

#### 7-(b).

$(t_{{0.025}, 47})\sqrt{MSE}\sqrt{\frac{1}{n} + \frac{(33.7-39.52)^2}{SSX}} = (2.011741)(5.272538) = 10.60698$

$\implies \hat{\beta_1} \pm 10.60698$

$\therefore  [-16.58458, 4.62938]$
