---
output: pdf_document
---

## B27 \
Hector G. FLores Rodriguez

### Stats 110 - HW5 \
November 13, 2017

<br>

### 1. 3.23
```{r}
# Load data
diamonds = read.csv("../data/Diamonds.csv")
```

<br>

#### 1-(a). Quadratic model using Depth
```{r}
model_a = lm(TotalPrice ~ Depth + I(Depth^2), data=diamonds)
summary(model_a)
```

<br>

#### 1-(b). Two-predictor model using Carat and Depth
```{r}
model_b = lm(TotalPrice ~ Carat + Depth, data=diamonds)
summary(model_b)
```

<br>

#### 1-(c). A three-predictor model that adds interaction for Carat and Depth
```{r}
model_c = lm(TotalPrice ~ Carat + Depth + Carat*Depth, data=diamonds)
summary(model_c)
```

<br>

#### 1-(d). Complete second-order model using Carat and Depth.
```{r}
model_d = lm(TotalPrice ~ Carat + Depth + I(Carat^2) + I(Depth^2) + Carat*Depth,
             data=diamonds)
summary(model_d)
```

The quadratic model where CaratSq is the quadratic term provides the better model. The model captures most of the variance yet it is a more parsimonious model than the second order model and the three predictor model with the interaction term. 

<br>

### 2. Exercise 3.24

```{r}
my_model = lm(TotalPrice ~ Carat + I(Carat^2), data=diamonds)
summary(my_model)
```

<br>

#### 2-(a). Check for homoscedacity and normality
```{r}
par(mfrow=c(1,2))
residuals = rstandard(my_model)
plot(residuals)
qqnorm(residuals)
qqline(residuals)
```

There is heteroskedacity and a lack of normality in my model.

<br>

#### 2-(b). Transform response variable to natural log
```{r}
log_model = lm(log(TotalPrice) ~ Carat + I(Carat^2), data=diamonds)
summary(log_model)
```
My "best" choice of predictors is still a reasonable choice for predicting logPrice.

#### 2-(c). Check graphs for log model
```{r}
par(mfrow=c(1,2))
residuals2 = rstandard(log_model)
plot(residuals2)
qqnorm(residuals2)
qqline(residuals2)
```
The log transformation helped with heteroskedacity and normality. The assumptions are now fairly reasonable.

<br>

### 4. Exercise 3.25
Use nested F-test for the complete second-order model to determine if all the terms in the model that involve Depth could be removed withought signifcantly impairing its effectiveness.

<br>

```{r}
full_model = model_d
reduced_model = my_model
anova(reduced_model, full_model)
```

There exist some term that involves information on Depth that is significant.

<br>

### 4. Exercise 3.26
Couple found a 0.5-carat diamond with depth of 62%.

#### 4-(a). Determine average total price for quadratic model

```{r}
new_diamond = data.frame(Carat=0.5, Depth=62.0)
predict(my_model, new_diamond)
```

The quadratic model predicts $1794.84 as the average total price.

<br>

#### 4-(b). 95% confidence interval for the mean total price
```{r}
predict(my_model, new_diamond, interval="c")
```

With 95% confidence, the mean total price for a 0.5-carat diamond with a depth of 62% somewhere between $1424.30 and $2165.40

#### 4-(c). 95% prediction interval
```{r}
predict(my_model, new_diamond, interval="predict")
```
With 95% confidence, we predict that the total price for a 0.5-carat diamond with depth of 62% is somewhere between $0 and $5994.15

**Note**: Negative dollars or recieving money for purchasing a diamond doesn't make sense.

<br>

#### 4-(d). Repeat two intervals for logPrice
```{r}
exp(predict(log_model, new_diamond, interval="c"))
```

With 95% confidence, the mean total price for a 0.5-carat diamond with a depth of 62% somewhere between $1784.59 and $1938.91

```{r}
exp(predict(log_model, new_diamond, interval="p"))
```

With 95% confidence, we predict that the total price for a 0.5-carat diamond with depth of 62% is somewhere between $1162.65 and $2976.09
